Java Based Memory Latency Simulator

### 2020-11-17 finalPaper/paper.tex
Updated stats gathering section

Explain every statistic. 
Also describe components and terms as you go.

>>>>

Explain every statistics.

As we will be simulating the momeory simulator, we will be working on the virtual
components. These components are those linked directly with the memory usage, these will
include the central processing unit (CPU), the Hard Drive and the RAM sticks.
Throughout the simulation the CPU will be accessing the RAM and the Hard Drive to process
the data exxisting in both of these components. We are going to be timing the transfer
of data from both the Hard Drive and RAM.

The movement, reading and writing of the data to any of the components will be timed, which
will help us collect the major statistics we need here. The latency which is going to be the
major finding of the simulation is going to be calculted throught a stopwatch implemented
inside our program. As we keep clocking, the time is going to be a projected ratio of the time that will be taking
place on the basic level. Thus, the time will be reduced to the ratio fully suited for the
level of details being dealt with in the simulator.

The Memory, which is the core component of the simulator will be represented by array of bytes and
will be

The variable we are going to have in the simulation are going to be the number of Cores in the CPU,
the number of hard drives, the size of hard drive in bytes, the number of RAM sticks, the size of
each of the RAM stick and the size of the CPU Cache. The values for each of these variables are
going to be input by the user of the simulator, before the program starts simulating the events.
The simulator is programmed in a way that different values for any these variables are going to effect
the statistics from a minor to a very significant way, depending upon the value of change and the
effectiveness of the change in the study.

CPU is going to have an option to be variable in number of cores, but for the path of the study being
conducted we are going to mantain the number of cores to just 1 throughout. Apart from the number
of cores, CPU will have a

Also describe components and terms as you go.
